%\usepackage{geometry}  % for easy margin settings
%% margins setting // NCKU內頁設定 // cbj
%\geometry{verbose,a4paper,tmargin=2.3cm,bmargin=3.5cm,lmargin=2.5cm,rmargin=3cm}

\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage{times}
\usepackage{verbatim}
\usepackage{color}
\usepackage{url}
\usepackage{graphicx}
\usepackage{array}
\usepackage{wallpaper}
\usepackage{pdfpages}
\usepackage{indentfirst}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{enumitem}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{tabularx}
% Title
\title{Adaptive Load-balancing Scheme Through Wireless SDN-based Association Control}

% Author
\author{
	\IEEEauthorblockN{
		Chia-Ying Lin, 
		Wan-Ping Tsai, 
		Meng-Hsun Tsai and
		Yun-Zhan Cai	}
	\IEEEauthorblockA{
		Department of Computer Science and Information Engineering, National Cheng Kung University,\\
		Tainan, Taiwan\\
		Email: \{a711186, wanping\}@imslab.csie.ncku.edu.tw, tsaimh@csie.ncku.edu.tw, F74039017@mail.ncku.edu.tw
	}
}



\begin{document}

\maketitle

\begin{abstract}
%In WLAN, due to the popularity of mobile users, 
As the popularity of mobile applications, Wi-Fi has become one of the major access methods for many users.
% utilization has increased a lot. 
%One of the critical issues is that 
When a large amount of users move in public places together, such as classrooms or meeting rooms, severe load imbalance of Wi-Fi Access Points (APs) and unfair bandwidth allocation are likely to occur consequently.

%Software Defined Network (SDN), proposed by the Stanford University, separates the control modules, which are managed by centralized controllers, from the infrastructure layer. SDN is programmable. SDN allows the network administrators to write programs on the controllers.
Software Defined Networking (SDN) is a new networking paradigm which allows the network administrators to write programs for controlling the behaviors of network devices.
In this paper, 
we propose an adaptive load balancing scheme through association control in wireless software defined network. 
%We design a system model which 
The proposed scheme consists of an event detection mechanism and an adaptive load balancing algorithm on controller. 
In our algorithm, controller can derive an optimal association solution 
%by computing the load and user number of APs. 
based on the traffic load and number of users on each AP. 
To observe the effects of population distribution and user mobility, we propose a simulation model to investigate the performance in terms of average AP load, user bandwidth and user throughput. 
Our simulation results show that our scheme has better performance than other three methods and performs better in imbalanced environment.

\end{abstract}

% {\bf Keywords}: association control, IEEE 802.11 network, load balancing, SDN
\begin{IEEEkeywords}
association control; IEEE 802.11 network; load balancing; SDN

\end{IEEEkeywords}

\section{Introduction} \label{ch:1-introduction}
	\input{sec1.tex}

\section{Related Works} \label{ch:2-background}
	\input{sec2.tex}

\section{Proposed Scheme} \label{ch:3-proposed}
	\input{sec3.tex}
	
\section{Performance Evaluation} \label{ch:5-performance}
	\input{sec4.tex}
	
\section{Conclusions} \label{ch:6-conclusion}
	\input{sec5.tex}

% use section* for acknowledgment
\section*{Acknowledgment}
%The authors would like to thank...
This work was sponsored in part by Ministry of Science and Technology (MOST), Taiwan, under the contract number MOST 105-2221-E-006-186- and MOST 105-2815-C-006-108-E. 

\bibliographystyle{IEEEtran}
\bibliography{reference}	
	
\end{document}

